---
title: "Group_Project_1"
output:
  word_document: default
  html_notebook: default
  pdf_document: default
---

##TITLE PAGE

#Install all packages necessary:
```{r}
library(tidyverse)
library(car)
library(devtools)
install_github("nxskok/smmr")
library(smmr)
```

##Introduction:
Refer to report example Ken has in Assignment 6. Ctrl+F, "Introduction".

#Read in the data:
```{r}
url="http://www.utsc.utoronto.ca/~butler/c32/restaurant-tips.txt"
#Since values are separated by tab characters, the suitable function to read the data file is read_tsv().
tips=read_tsv(url)
tips
```

#Assess relationship between Server vs. PctTip, Server vs. Tip:
```{r}
ggplot(tips,aes(sample=PctTip,color=Server))+stat_qq()+stat_qq_line()+facet_wrap(~Server,scale="free",ncol=2)
median_test(tips,PctTip,Server)

ggplot(tips,aes(sample=Tip,color=Server))+stat_qq()+stat_qq_line()+facet_wrap(~Server,scale="free",ncol=2)
median_test(tips,Tip,Server)

#t.server.aov=aov(PctTip~Server,data=tips)
#summary(t.server.aov)
```
Conclusion: The average (median) tip amount and tip percentage are the same for all three servers.

#Assess relationship between Day vs. PctTip, Day vs. Tip:
```{r}
ggplot(tips,aes(sample=PctTip,color=Day))+stat_qq()+stat_qq_line()+facet_wrap(~Day,scale="free",ncol=3)
median_test(tips,PctTip,Day)

ggplot(tips,aes(sample=Tip,color=Day))+stat_qq()+stat_qq_line()+facet_wrap(~Day,scale="free",ncol=3)
median_test(tips,Tip,Day)

#t.day.aov=aov(PctTip~Day,data=tips)
#summary(t.day.aov)
```
Conclusion: The average (median) tip amount and tip percentage are the same for all days of the week. 

#Assess relationship between Guests vs. PctTip, Guests vs. Tip:
```{r}
ggplot(tips,aes(sample=PctTip,color=factor(Guests)))+stat_qq()+stat_qq_line()+facet_wrap(~factor(Guests),scale="free",ncol=3)
median_test(tips,PctTip,factor(Guests))

ggplot(tips,aes(sample=Tip,color=factor(Guests)))+stat_qq()+stat_qq_line()+facet_wrap(~factor(Guests),scale="free",ncol=3)
median_test(tips,Tip,factor(Guests))

#t.day.aov=aov(PctTip~Day,data=tips)
#summary(t.day.aov)
```
Conclusion: The average (median) tip amount differs between the number of guests, while the average (median) tip percentage are the same for all number of guests.

```{r}
pairwise_median_test(tips,Tip,Guests)
```
Conclusion: The two pairs of Guests that are significant are 1 vs. 2 and 1 vs. 3.

#Investigate why Guests is significant for Tip, but not for PctTip:
```{r}
tips %>% group_by(factor(Guests)) %>% summarize(mean_tip=mean(Tip),mean_bill=mean(Bill),mean_pcttip=mean(PctTip))
```
Comment: The average tip amount based on the number of guests ranges from $2.45 to $10, which is 5 times the difference. The average tip percentage ranges from 16.12% to 17.5%, which is only a 1-point difference. Thus, only the average (median) tip amount differs between the number of guests. 

#Assess relationship between Credit vs. PctTip, Credit vs. Tip:
```{r}
ggplot(tips,aes(sample=PctTip,color=Credit))+stat_qq()+stat_qq_line()+facet_wrap(~Credit,scale="free",ncol=3)
median_test(tips,PctTip,Credit)

ggplot(tips,aes(sample=Tip,color=Credit))+stat_qq()+stat_qq_line()+facet_wrap(~Credit,scale="free",ncol=3)
median_test(tips,Tip,Credit)

#t.credit.aov=aov(PctTip~Credit,data=tips)
#summary(t.credit.aov)
```
Conclusion: The average (median) tip amount and tip percentage differs between the two methods of payment. 

```{r}
pairwise_median_test(tips,PctTip,Credit)
pairwise_median_test(tips,Tip,Credit)
```
Conclusion: The pair of payment methods are significant, with Tip having a much smaller p-value #Explain why (1 sentence). This is consistent for the following tests. 

#Assess relationship between Bill vs. PctTip:
```{r}
#Split `Bill` by quartile ranges.
summary(tips$Bill)
```
Comment: We split values of `Bill` into four ranges 1,2,3,4:
Range 1: values <= Q1=15.19.
Range 2: Q1=15.19 < values <= Q2=20.22.
Range 3: Q2=20.22 < values <= Q3=28.84.
Range 4: Q3=28.84 < values.

```{r}
#Create new column to dataframe that identifies which range the Bill value belongs to.
tips %>% mutate(Range = ifelse(Bill <=15.19, "1", ifelse(Bill <=20.22, "2", ifelse(Bill <=28.84, "3","4")))) -> bill_range
bill_range
```

```{r}
#Compute median test for `Bill` vs. `PctTip`.
ggplot(bill_range,aes(sample=PctTip,color=factor(Range)))+stat_qq()+stat_qq_line()+facet_wrap(~factor(Range),scale="free",ncol=3)
median_test(bill_range,PctTip,factor(Range))

ggplot(bill_range,aes(sample=Tip,color=factor(Range)))+stat_qq()+stat_qq_line()+facet_wrap(~factor(Range),scale="free",ncol=3)
median_test(bill_range,Tip,factor(Range))

#t.bill.aov=aov(PctTip~Bill,data=bill_range)
#summary(t.bill.aov)
```
Comment: Since the average (median) tip amount and tip percentage differs between the bill ranges, we investigate which range is different from which.

```{r}
pairwise_median_test(bill_range,PctTip,Range)
pairwise_median_test(bill_range,Tip,Range)
```
Conclusion: All pairs of bill ranges are significant.

##Conclusion:
Significant variables: Guests vs Tip (only pairs 1-2, 1-3), Credit vs PctTip, Credit vs Tip, Bill range vs PctTip, Bill range vs Tip. 
